Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-08-04 LaTeX/Turnover.tex
first draft of new figures done (without sally's type)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Heterogametic transitions with/without sex ratio change
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\begin{tikzpicture}[remember picture]
	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
\end{tikzpicture}
\caption{
%\textcolor{red}{Is this what Sally was thinking?}
%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here. Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY. Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}. }
%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
A neo-Y invades (panel B) a population with an equal sex ratio. 
With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
}
\label{fig:Combination_Turnover_Ratio}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

@@

%Chromosomal Positions
\begin{figure}[!h]
%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
%\includegraphics[width=\linewidth]{PositionPlot}\\
\begin{tikzpicture}[remember picture]
%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
\end{tikzpicture}
\caption{
Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
% (neo-Y invading ZW in black, neo-W invading XY in red)
%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$; gray region).
In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.   
In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$). 
%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}). 
%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$). 
%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\ 
%\textcolor{red}{
%1. I suspect that panel C has a region where no equilibrium is maintained (CHECK! Maybe include different parameters here or remove the part when no equilibrium). MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
%\\
%2. Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure). MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B

@@

}
\label{fig:Combination_Centimorgans}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Haplotype invasion region plot
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\begin{tikzpicture}[remember picture]
	\node[] () {
	\includegraphics[width=0.5\linewidth]{regionplot_2a}
	\includegraphics[width=0.5\linewidth]{regionplot_hap}
	};
\end{tikzpicture}
\caption{
Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
}
\label{fig:regionplot_2a}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
\caption{
In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
}
\label{fig:SexAntagTighter}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.45\linewidth]{regionplot_2a}
\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
\caption{
In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
}
\label{fig:BothOverdominance}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
\caption{
With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
}
\label{fig:LooseDecline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%A neo-W can invade an XY system under a large number of selective regimes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{PositionPlot_4}
\caption{
 A neo-W can invade an XY system under a large number of selective regimes.
In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.   
In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
}
\label{fig:Combination_Centimorgans}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
\caption{
Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
}
\label{fig:SexRatioBad}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Haploid selection can lead to polymorphic SD systems 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{Polymorphic}
\caption{
Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = -1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.   
}
\label{fig:Polymorphism}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%CYCLES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
\caption{
Thought I'd show this just for fun (not for publication).
}
\label{fig:Cycles}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Heterogametic transitions with/without sex ratio change
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\begin{tikzpicture}[remember picture]
%	\node[] (plot) {\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}};
%	\node[above = -1cm of plot, xshift = -100] () {XY $\rightarrow$ ZW};
%	\node[above = -1cm of plot, xshift = 90] () {ZW $\rightarrow$ XY};
%\end{tikzpicture}
%\caption{
%%\textcolor{red}{Is this what Sally was thinking?}
%%\textcolor{blue}{I think this works but I'm confused as to why the speed of spread should be so much different for XY and ZW here. Figure \ref{fig:Combination_Turnover} and \ref{fig:Combination_Centimorgans} suggests that there's not much difference between XY->ZW and ZW->XY. Maybe we should just stick with the 4 cases in figure \ref{fig:Combination_Turnover}. }
%%\textcolor{red}{i messed up and had $r=0.5$ instead of $r=0.05$ for B and D. haven't fixed fitness plot below.}
%Heterogametic transitions occur (panels A and B) regardless of sex ratio biases (panels C and D).
%A neo-W invades (panel A) and equalizes the male-biased sex ratio (panel C) that was caused by meiotic drive in males.
%A neo-Y invades (panel B) a population with an equal sex ratio. 
%With any amount of linkage ($R<1/2$), the neo-Y becomes associated with the driving allele in males, and in the end causes a male bias.
%Parameters: $s^\female = s^\male = 1/5$, $h^\female = h^\male = 7/10$, $t^\female = t^\male=0$, $\alpha^\female_\Delta = 0$, $\alpha^\male_\Delta = -1/5$, $r = 1/20$.
%}
%\label{fig:Combination_Turnover_Ratio}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

@@

%%Chromosomal Positions
%%\includegraphics[width=\linewidth]{Combination_Centimorgan}\\
%%\includegraphics[width=\linewidth]{PositionPlot}\\
%\begin{tikzpicture}[remember picture]
%%	\node[] () {\includegraphics[width=\linewidth]{PositionPlot}};
%	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
%%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
%%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
%%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
%%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
%%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
%%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
%%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
%%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
%%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);
%\end{tikzpicture}
% A neo-W can invade an XY system under a large number of selective regimes.
%%Invasion fitness of a neo-sex-determining allele against the relative genomic location of a locus under direct selection. 
%% (neo-Y invading ZW in black, neo-W invading XY in red)
%%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
%%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
%In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B).
%In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.   
%In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event.    
%%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 
%%A polymorphism can then be maintained by opposing selection between the haploid and diploid phases. 
%%In B, there is drive in favour of the $a$ allele in males ($\alpha^\male_{\Delta}=-1/20$), no female meiotic drive or gametic competition, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), and equal selection in diploid sexes ($s^\female=s^\male=1/10$, $h^\female=h^\male=7/10$). 
%%In this case, a neo-W can invade even when the selected locus is more closely linked to the ancestral sex determining locus (see Table \ref{tab:specialcases} and Figure \ref{fig:Combination_Turnover}). 
%%In C and D, there is gametic competition among male gametes only (favouring $a$, $t^\male=-1/10$) and no meiotic drive or gametic competition in females ($t^\female=\alpha^\Hermaphrodite_{\Delta}=0$). 
%%In this case, the neo-W does not invade if $s^\female>s^\male$ (panel C: $s^\female=3/20$, $s^\male=1/20$) but does if $s^\female<s^\male$ (panel D: $s^\female=1/20$, $s^\male=3/20$), see Table \ref{tab:specialcases}.\\ 
%%\textcolor{red}{
%%1. I suspect that panel C has a region where no equilibrium is maintained (CHECK! Maybe include different parameters here or remove the part when no equilibrium). MMO: If you trust the sieve function there are stable equilibria across the entire range, although they differ greatly between XY and ZW systems near -25cM.
%%\\
%%2. Currently use different parameters for B than using in figure \ref{fig:Combination_Turnover} (selection/drive twice as strong in turnover figure). MMO: this is to keep it within the bounds of the plot -- using the same parameters as figure 1 makes the peak at -25 reach roughly 0.1, and then it is difficult to see the details of A,C, and D.
%%%This plot would also benefit from titles giving, e.g., ``sexually-antagonistic selection, $s^\female s^\male<0$'' for A, ``male meiotic drive, $s^\female s^\male>0$'' for B
%%}

@@

%\label{fig:Combination_Centimorgans}
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Haplotype invasion region plot
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\begin{tikzpicture}[remember picture]
%	\node[] () {
%	\includegraphics[width=0.5\linewidth]{regionplot_2a}
%	\includegraphics[width=0.5\linewidth]{regionplot_hap}
%	};
%\end{tikzpicture}
%\caption{
%Parameter space (gray) where both neo-W haplotypes can invade from the same stable resident $r=0$ equilibria (equations \ref{eq:tightequil}), and therefore where an unlinked neo-W can invade an XY system with perfect sex-linkage.
%\textbf{A}, In the absence of haploid selection, both neo-W haplotypes can invade for much of the parameter space where the relative fitnesses of male homozygotes, $w_{AA}^\male$ and $w_{aa}^\male$, are both less than that of the heterozygote, $w_{Aa}^\male = 1$.
%In the white region neo-W haplotypes paired with the allele fixed on the Y cannot invade.
%Parameters as in \cite{Otto2014} Figure 2a: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\Hermaphrodite=1/2$, $w_{Aa}^\Hermaphrodite=1$, and $w_{AA}^\female=w_{aa}^\female=0.75$.
%\textbf{B}, When selection is the same in both diploid sexes ($w_{aa}^\Hermaphrodite = 1$, $w_{Aa}^\Hermaphrodite = 1 + h s$, $w_{AA}^\Hermaphrodite = 1+s$), both neo-W haplotypes can invade over a portion of the parameter space where selection in diploids ($s$) opposes the force of drive during meiosis in males ($\alpha_{\Delta}^\male$).
%Parameters: $w_A^\Hermaphrodite=w_a^\Hermaphrodite$, $\alpha^\female=1/2$, $h=1/2$.
%}
%\label{fig:regionplot_2a}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
